---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r}
library(tidyverse)
library(scales)
```


# pvErhard

<!-- badges: start -->
<!-- badges: end -->

Provide the data necessary to calculate the Erhard RKV valves.

## Installation

You can install the development version of pvErhard like so:

``` r
remotes::install_github("ratral/pvErhard")
```

## Zeta $\zeta$ and flow coefficient $K_{vs}$ values of the ERHARD RKS Valves at a fully-open valve

The $K_{vs}$ value expresses the amount of flow in a regulating valve at a fully-open valve position and a pressure differential of 1 bar.  The $K_{vs}$ value is a special case of the $K_{vs}$ value, which indicates the flow at a given valve position and a pressure differential of 1 bar. 

```{r example}
library(pvErhard)

```



```{r, echo = FALSE}
pvErhard %>% 
  ggplot(aes(x = kvs, y = reorder(id, kvs))) +
  geom_point(color='red',fill='steelblue') +
  scale_y_discrete(name="Valve Type") +
  scale_x_log10(name="Kvs Value (m3/h)") +
  annotation_logticks(sides="b") + 
  labs( title = "Flow coefficient ERHARD RKS Valves in (m3/h)") +
  theme_bw()
```


```{r, echo = FALSE}
pvErhard %>% 
  ggplot(aes(x = zvs, y = reorder(id, zvs))) +
  geom_point(color='red',fill='steelblue') +
  scale_y_discrete(name="Valve Type") +
  scale_x_continuous(name="Zeta Value", limits=c(0, 10), breaks=1:10)+
  labs( title = "Zeta value ERHARD RKS Valves") +
  theme_bw()
```


